Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\

### 2019-04-30 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

If our algorithm does not find a feasible solution among the item of equipment that were provided to our synthesis algorithm, then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution. It indicates that was not possible to combine the itens of each equipment and create a feasible solution. The main challenge for the verification part is to find a feasible solution (technically speaking, regarding the constraints and user requirements), which is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is provided to our synthesis algorithm. \textcolor{red}{An unfeasible solution happens due to the incomplete list of equipment?}
%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------
We have performed two case studies to evaluate the proposed approach of optimization as described in Table~\ref{tab1}. Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification}: CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used to compare the approach effectiveness and efficiency. The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}. All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. The experiments were performed with a predefined timeout of 240 minutes.

Only CPAchecker could present the optimal sizing of the two case studies: the result came in 66 minutes and 35 minutes, respectively. %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code. 
CBMC and ESBMC had UNKNOWN result (timeout or out of memory).

@@

More experimentation will be performed with more case studies and to compare the result with some off-the-shelf software that focus on sizing and optimization. Besides, it will be inputted a larger number of components (panels, batteries, controllers and inverters) to the database.
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{trindadeThesis}{}

>>>>

If our algorithm does not find a feasible solution among the item of equipment that were provided to our synthesis algorithm, then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution. It indicates that was not possible to combine the itens of each equipment and create a feasible solution. The main challenge for the verification part is to find a feasible solution (technically speaking, regarding the constraints and user requirements), which is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is provided to our synthesis algorithm. \textcolor{red}{An unfeasible solution happens due to the incomplete list of equipment?}

\textcolor{red}{Could you please reinforce here that our approach is sound and completely automated?}

%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------

We have performed two case studies to evaluate our proposed synthesis approach as described in Table~\ref{tab1}. Furthermore, three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used to compare our approach effectiveness and efficiency. The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}. All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. The experiments were performed with a predefined timeout of $240$ minutes.

Only CPAchecker could present the optimal sizing of the two case studies: the result came in 66 minutes and 35 minutes, respectively. %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code. 
CBMC and ESBMC produced UNKNOWN result (timeout or out of memory).

@@

For future wore, we will perform additional experiments using other case studies and also compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization. 
Furthermore, we will be provide a larger number of components (panels, batteries, controllers and inverters) to our database to be used by our synthesis engine.

\textcolor{red}{We have to abbreviate our references. Take a look at https://ssvlab.github.io/lucasccordeiro/papers/icse2011.pdf, e.g., I've just put the conference acronym, remove conference place (New York), etc}

% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{trindadeThesis}{}
